%%----------------------------------------------------------------------
%%----------------------------------------------------------------------
\clearpage
\missiontitle{Common Rules}

\begin{columns}
%The following rules are to be applied to each mission.
  
\missionheading{Startup Sequence}

The start of each game proceeds as follows unless the mission or event
rules note otherwise:

\begin{enumerate}\shortlist
\item Clarify terrain and mission rules

\item Both players share their army lists

\item Determine warlord traits, then psychic powers, and then other
  pre-game effects and choices

\item D6 roll off to select deployment zones

\item Place primary objective markers

\item D6 roll off to choose first or second deployment

\item Deploy main armies in that order

\item Deploy any Infiltrators (pg. 167)

\item Secretly choose and record secondary objectives from the options
  available for the mission

\item Make any Scout redeployments (pg. 171)

\item Reveal secondary objectives and any related selections or marker
  placements as directed

\item First to deploy chooses to play first or second

\item Seize the Initiative roll, if desired and permitted

\item \emph{Battle!}
\end{enumerate}

Standard objective placement constraints apply
unless noted otherwise by a specific mission.

\missionheading{Game Rules}

The Invisibility psychic power is amended to be:

\begin{itemize}\shortlist
\item Invisibility is a blessing that targets a single friendly unit
  within 24". While the power is in effect, enemy units shooting at
  the target unit do so at BS 1, and in close combat will only hit
  models of the target unit on To Hit rolls of 5+.
\end{itemize}

% For any failed 2+ save that may be rerolled, the reroll only
% succeeds on a 4+.

Objective markers may be controlled or contested by models/units up to
3" horizontally from the side edge of the marker and 6" vertically
from its bottom face. Markers should all be the same size (typically
equivalent to a 40mm base).

\vfill\vbox to 0pt{}
\columnbreak
\missionheading{Mission Rules}

The following apply in each mission by default.

\vspace*{-10pt}%
\nightfighting

\vspace*{-10pt}%
\missionsubheading{Easy Recon.}  Players add~+1 to their roll to
choose first or second deployment for each superheavy vehicle or
gargantuan creature in the opposing army. Players with~3 or more
superheavy vehicles or gargantuan creatures cannot Seize the
Initiative.

\vspace*{-10pt}%
\missionsubheading{Reserves.} As defined on page~135 of the main
\emph{Warhammer 40,000} rulebook.

\vspace*{-10pt}%
\missionsubheading{Seize the Initiative.} As defined on page~132 of
the main \emph{Warhammer 40,000} rulebook.

\vspace*{-10pt}%
\missionsubheading{Variable Game Length.} As defined on page~133 of
the main \emph{Warhammer 40,000} rulebook.

\vspace*{-10pt}%
\missionsubheading{All In.}  Units/models in reserve at game end count
as completely destroyed/removed as a casualty.


\missionheading{Tertiary Objectives}

The following tertiary objectives apply in each mission.
\underline{At most~5 total victory points may be earned by a}
\underline{player across all of the tertiary objectives.}

\vspace*{-1pt}%
\begin{itemize}
\item \textit{Victory Through Attrition.}  Score~1 victory point for
  every~2 unsaved hull points or wounds suffered by an opposing
  superheavy vehicle or gargantuan creature through any means,
  including explosions and other indirect effects.  These points are
  earned at the end of any phase in which such damage occurs, and thus
  include any repaired or regenerated later.

\vspace*{-10pt}%
\item \textit{Lord of Nothing.}  Score~2 victory points at game end
  for each opposing Lord of War character removed as a casualty or
  falling back.

\vspace*{-10pt}%
\item \textit{Slay the Warlord.}  At game end, score~2 victory points
  in standard games and 1 victory point in team games for each
  opposing warlord removed as a casualty or falling back.

\vspace*{-10pt}%
\item \textit{Linebreaker.}  Score~2 victory points if a model from
  any friendly scoring unit is completely within 12'' of your
  opponent's table edge.

\vspace*{-10pt}%
\item \textit{First Blood.}  As defined on page~133 of the main
  \emph{Warhammer 40,000} rulebook.

\vspace*{-10pt}%
\item \textit{Special Conditions.}  Any unit, faction, formation, or
  other special rules granting victory points to either player are
  considered tertiary objectives and are included within the~5 point
  cap.
\end{itemize}

\vfill\vbox to 0pt{}
\end{columns}
