\missionheading{Doubles Rules}

The following rules apply in doubles games.

Both players select and field separate army lists. Teammates consider
their partner's units and models to be allies of convenience to their
own army. Both players on a team nominate a warlord for themselves.

If one or both players in a team field Chaos Daemons, the team rolls
once on the Warp Storm table.  The effects do not apply to either
player's army unless specifically dictated by the table, e.g.,
targeting Chaos Daemons or particular marks.

% The (Codex: Chaos Daemons) do not affect their teammate's army and
% models unless specifically dictated by the table, e.g., targeting
% specific marks.  The Warp Storm table is only rolled once per team.

In the psychic phase, a single D6 is rolled to determine the base warp
charge from which each of the four players generate their own
individual pools, applying the usual rules.  Players all use their own
warp charge pool; teammates cannot combine or share warp
charge. Either opposing player with models on the table may attempt to
deny the witch, caveat that if a specific unit of enemy models is
targeted, their player alone may attempt to block the spell.

Units may not shoot at close combats even if none of their player's
units are engaged.

Teams are not eliminated unless there are no models of either member
on the table.

For all other gameplay purposes the combined forces of a team are
considered a single army comprised of multiple detachments, and the
team considered a single player for all rules.
