\toblocktitle*

\begin{toblock}
  \tocard{Frontfield \raisebox{6pt}{$\dagger$}}{When first put in
    play, choose a marker in your opponent's deployment zone.  At the
    end of your turns while in play, mark one of these boxes if you
    control that objective: \hfill $\Box$ $\Box$ $\Box$
    $\Box$\newline%
    \hbox to 0pt{}\hfill\emph{Value:} 1 mission point for each marked
    box.}{X}%
%
  \tocard{Midfield \raisebox{6pt}{$\dagger$}}{When first put in play,
    choose a marker in neither deployment zone.  At the end of your
    turns while in play, mark one of these boxes if you control that
    objective: \hfill $\Box$ $\Box$ $\Box$ $\Box$\newline%
    \hbox to 0pt{}\hfill\emph{Value:} 1 mission point for each marked
    box.}{X}%
%
  \tocard{Backfield \raisebox{6pt}{$\dagger$}}{When first put in play,
    choose a marker in your deployment zone.  At the end of your turns
    while in play, mark one of these boxes if you control that
    objective: \hfill $\Box$ $\Box$ $\Box$ $\Box$\newline%
    \hbox to 0pt{}\hfill\emph{Value:} 1 mission point for each marked
    box.}{X}%
%
%
  \tocard{Conqueror \raisebox{6pt}{$\dagger$}}{When first put in play,
    your opponent nominates two markers, of which you choose one.  At
    the end of your turns while in play, mark a box if you control
    that objective: \hfill $\Box$ $\Box$ $\Box$ $\Box$\newline%
    \hbox to 0pt{}\hfill\emph{Value:} 1 mission point for each marked
    box.}{X}%
%
  \tocard{Defender \raisebox{6pt}{$\dagger$}}{When first put in play,
    you nominate two markers, of which your opponent chooses one.  At
    the end of your turns while in play, mark a box if you control the
    chosen objective: \hfill $\Box$ $\Box$ $\Box$ $\Box$\newline%
    \hbox to 0pt{}\hfill\emph{Value:} 1 mission point for each marked
    box.}{X}%
%
  \tocard{Warrior}{When first put in play, your opponent nominates 3
    of their units.  Mark a box whenever one of those units is removed
    from play: \hfill $\Box$ $\Box$ $\Box$\newline%
    \hbox to 0pt{}\hfill\emph{Value:} 2 mission points for each
    marked box.}{X}%
\end{toblock}


\bigskip%
\begin{toblock}
  \tocard{Butcher}{While in play, mark one of these boxes each time an
    opposing non-vehicle, originally multi-model unit is removed from
    play: \hfill $\Box$ $\Box$ $\Box$ $\Box$\newline%
    \hbox to 0pt{}\hfill\emph{Value:} 1 mission point for each marked
    box.}{X}%
%
  \tocard{Hunter}{While in play, mark one of these boxes each time an
    opposing vehicle or monstrous creature is removed from play:
    \hfill $\Box$ $\Box$ $\Box$ $\Box$\newline%
    \hbox to 0pt{}\hfill\emph{Value:} 1 mission point for each marked
    box.}{X}%
%
  \tocard{Purifier}{While in play, mark one of these boxes each time
    an opposing unit with the Psyker, Psychic Pilot, or Brotherhood of
    Psykers/Sorcerers special rule is removed from play: \hfill $\Box$
    $\Box$ $\Box$ $\Box$\newline%
    \hbox to 0pt{}\hfill\emph{Value:} 1 mission point for each marked
    box.}{X}%
%
  \tocard{Assassin}{While in play, mark one of these boxes each time
    an opposing character is removed from play: \hfill $\Box$ $\Box$
    $\Box$ $\Box$\newline%
    \hbox to 0pt{}\hfill\emph{Value:} 1 mission point for each marked
    box.}{X}%
%
  \tocard{Harasser}{Contest or claim as many markers as possible;
    cannot score Turn 1.\newline%
    \hbox to 0pt{}\hfill\emph{Value:} 4 mission points minus
    the\newline \hbox to 0pt{}\hfill number of markers controlled by
    your opponent, to a minimum of 0.}{X}%
%
  \tocard{Commander}{Claim as many markers as possible; cannot score
    Turn 1.\newline%
    \hbox to 0pt{}\hfill\emph{Value:} 1 mission point for each marker
    you control.}{X}

\end{toblock}
